Greenhouse gas emissions model - making scenarios

### 2021-11-11 Scenarios_report.Rmd
not working yet...

```{r}
scenarios<-read.table("data/scenarios.csv", sep = ",", fileEncoding = "UTF-8-BOM")

@@

scenarios<-data.frame(Variable=variables_to_update,param="both")

@@

>>>>

```{r}
scenarios<-read.table("data/scenarios.csv", sep = ",", fileEncoding = "UTF-8-BOM",header=TRUE)

@@

@@

variables_to_update<-c(paste0("N_animal_type_",1:12),"feeding_system")

scenarios<-data.frame(Variables=variables_to_update,param="both")
